Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-07 paper_latex_edit - Copy.tex
Adding BER to the system Model

>>>>

\subsection{Bit Error Rate Analysis with Compressed CSI}
Under imperfect CSI feedback, the reconstructed channel matrix $\hat{\tilde{\mathbf{H}}}_f$ contains errors from:
\begin{itemize}
    \item Channel estimation noise (AWGN)
    \item CSI compression artifacts
    \item Feedback quantization
\end{itemize}

The effective SNR at the receiver becomes:
\begin{equation}
    \text{SNR}_{\text{eff}} = \frac{\|\mathbf{H}\|^2 E_b}{N_0 + E_b(\sigma_e^2 + \sigma_q^2)}
\end{equation}
where $\sigma_e^2$ is CSI estimation error variance and $\sigma_q^2$ is quantization noise.

For BPSK modulation, the BER with compressed CSI is:
\begin{equation}
    \text{BER} \approx Q\left(\sqrt{\frac{2N_t\gamma}{1 + \gamma(\sigma_e^2 + \sigma_q^2)}}\right)
\end{equation}
where $Q(x)$ is the Q-function and $\gamma = E_b/N_0$.
